\documentclass{article}

%%%%%%%%%%%%%%%%%%%
% package imports %
%%%%%%%%%%%%%%%%%%%
\usepackage{fancyhdr}
\usepackage[hmargin=1.5cm, vmargin=0.75cm, includefoot]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor} 
\usepackage{fontspec}
\usepackage[absolute]{textpos}
\usepackage[UKenglish]{isodate}
\usepackage{titlesec}
\usepackage{twemojis}
\usepackage{fontawesome5}
\usepackage{multicol}

%%%%%%%%%%%%%%%%%%%%%
% Color Definitions %
%%%%%%%%%%%%%%%%%%%%%
\definecolor{date}{HTML}{666666} 
\definecolor{primary}{HTML}{2b2b2b}
\definecolor{nameheading}{HTML}{000000}
\definecolor{headings}{HTML}{000000}
\definecolor{subheadings}{HTML}{333333}

%%%%%%%%%%%%%%%%%%%%%%%
% Font Specifications %
%%%%%%%%%%%%%%%%%%%%%%%
\setmainfont[Color=primary, Path = fonts/lato/,BoldItalicFont=Lato-RegIta,BoldFont=Lato-Reg,ItalicFont=Lato-LigIta]{Lato-Reg}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text, Path = fonts/raleway/]{Raleway-Medium}
\NeedsTeXFormat{LaTeX2e}


%%%%%%%%%%%%%%%%%
% Date Commands %
%%%%%%%%%%%%%%%%%
\newcommand{\lastupdated}{
	\begin{textblock}{60}(155,5)
	\color{date}
	\fontspec[Path = fonts/raleway/]{Raleway-Regular}
	\fontsize{8pt}{10pt}
	\selectfont Last Updated on \today
	\end{textblock}
}

%%%%%%%%%%%%%%%%%
% Name Commands %
%%%%%%%%%%%%%%%%%
\newcommand{\namesection}[3]{
	\centering{
		\color{nameheading}
		\fontsize{18pt}{60pt}
		\fontspec[Path = fonts/lato/]{Lato-Hai}\selectfont #1 
		\fontspec[Path = fonts/poppins/]{Poppins-ExtraBold}
		\selectfont #2
	} \\[5pt]
	\centering{
		\color{headings}
		\fontspec[Path = fonts/raleway/]{Raleway-Medium}
		\fontsize{12pt}{14pt}\selectfont #3
	}
	\noindent\makebox[\linewidth]{
		\color{headings}
		\rule{1.0\linewidth}{1.0pt}
	}
	\vspace{-10pt}
}

\newcommand{\simpleheader}{
 	\noindent\makebox[\linewidth]{\color{headings}\rule{\paperwidth}{0.4pt}}
	\vspace{-15pt}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section separator Commands %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\titlespacing{\section}{0pt}{0pt}{0pt} 
\titlespacing{\subsection}{0pt}{0pt}{0pt}
\titlespacing{\subsubsection}{5pt}{0pt}{0pt}
\newcommand{\sectionsep}{\vspace{7pt}}
\newcommand{\subsectionsep}{\vspace{5pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section Commands %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Headings command
\titleformat{\section}{
	\color{headings}
	\scshape\fontspec[Path = fonts/poppins/]{Poppins-Black}\fontsize{15pt}{20pt}\selectfont \raggedright\uppercase
}{}{0em}{}

% Subheadings command
\titleformat{\subsection}{
	\color{subheadings}\raggedright\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{12pt}{14pt}\selectfont\bfseries\uppercase
}{}{0em}{}

\newcommand{\category}[1]{
	\color{subheadings}\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{11pt}{12pt}\selectfont\bfseries\uppercase {#1} \normalfont
}

% SubSubheadings command
\titleformat{\subsubsection}{
	\color{subheadings}\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{10pt}{14pt}\selectfont\bfseries\uppercase
}{}{0em}{}

% runsubsection command
\newcommand{\runsubsection}[1]{
	\color{subheadings}\fontspec[Path = fonts/lato/]{Lato-Bol}\fontsize{11pt}{14pt}\selectfont\bfseries\uppercase {#1} \normalfont
}

% Descriptors command
\newcommand{\descript}[1]{
	\color{subheadings}\raggedright\scshape\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{12pt}{14pt}\selectfont {#1 \\} \normalfont
}
\newcommand{\descriptList}[1]{
	\color{subheadings}\raggedright\scshape\fontspec[Path = fonts/lato/]{Lato-Reg}\fontsize{11pt}{14pt}\selectfont {#1 \\} \normalfont
}

% Location command
\newcommand{\location}[1]{
	\color{headings}\raggedright\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{10pt}{12pt}\selectfont {#1\\} \normalfont
}

% Bullet Lists with fewer gaps command
\newenvironment{tightemize}{
	\vspace{-\topsep}\begin{itemize}\itemsep1pt \parskip0pt \parsep0pt}
{\end{itemize}\vspace{-\topsep}
}

\newcommand{\datetag}[1]{
	\color{subheadings}\raggedright\scshape\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont {#1: \today \\} \normalfont
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header and Footer Settings %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\thepage}
\fancyfoot[L]{\today}

\renewcommand{\footrulewidth}{1.0pt}% default is 0pt

\begin{document}
%%%%%%%%%%%%%%%
%Title Section%
%%%%%%%%%%%%%%%

\namesection{}{Joji Joy}{ 
    \urlstyle{same}
    \href{email:email}{\twemoji[scale=0.4]{e-mail} jojijoy1512@gmail.com} |
     \twemoji[scale=0.36]{mobile phone} +91 8460247020 |
     \href{https://www.linkedin.com/in/joji-joy-jmj}{\faIcon{linkedin}  joji@linkedin} |
     \href{https://github.com/jojijoy15}{\faIcon{github}  joji@gihub}
}

%%%%%%%%%%%%%%%%%%%%
%Experience Section%
%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Western Union}
\descript{| Junior Associate, Solution Engineering}
\location{September 2022 - October 2022 | Pune, MH}
\begin{tightemize}
\item Contributed as a fullstack developer in compliance vertical application transformation team for Pharos, which is a compliance case management system developed using microservices architecture.
\item Experienced on event driven architecture and microservices patterns like Strangler, Listen to Yourself, Circuit Breaker.
\item Implemented design patterns to make reusable components and libraries for SpringBoot applications.
\item Designed and implemented solutions for business requirements as per  Agile practices in an enterprise setup.
\item Implemented Camunda 7 BPMN flow for case life cycle management as per business requirements.
\item Developed prototype application as part of exploring new Camunda 8  BPMN feature exploration.
\item Implemented UI features for Pharos application using Angular 17, Angular Material, NgRx and RxJs.
\item Reduced verification time by implementing Liquibase as change tracking tool for database schema changes.
\item Migrated Spring Boot from 2.x to 3.x for Spring Boot Applications.
\item Received recognition from Engineering Manager for consistent contribution and improvements delivered for Pharos application.
\end{tightemize}

\sectionsep

\runsubsection{ICE Mortgage Technology}
\descript{| SE 1, Platform Shared Services}
\location{March 2022 - July 2022 | Pune, MH}
\begin{tightemize}
\item As a backend developer, worked on Nodejs and Express based API gateway application.
\item Coordinated with architect for maintenance and improvement of API Gateway.
\end{tightemize}

\sectionsep

\runsubsection{Bajaj Finserv}
\descript{| Junior Software Developer, Platform Team}
\location{March 2021 – March 2022 | Pune, MH}
\begin{tightemize}
\item As a backend developer, implemented Rewards Framework from the ground up in microservices, event-driven architecture.
\item Developed highly performant REST APIs for Spring Boot applications written in Java 11. 
\item Worked on implementing choreography based SAGA microservice pattern to maintain database consistency across services, domain events were published  using AWS SNS and SQS.
\item Managed and revamped core Authentication service (Java 8) to improve performance of service by 30\%, by identifying better database indexes and code refactoring.
\item Coordinated with payment partners to integrate P2P service APIs.
\end{tightemize}

\sectionsep

\runsubsection{Matrix Comsec}
\descript{| Associate Software Developer, Telecom department}
\location{Dec 2018 – Sept 2019 | Vadodara, GJ}
\begin{tightemize}
\item As a C/C++ developer, worked on communication server backend.
\item Worked on Call Manager service and implemented features as per SRS for communication server.
\item Diagnosed and fixed bugs in the existing communication server backend.
\end{tightemize}

\section{Technical Skills}
\begin{tightemize}\vspace{7pt}
	\item\category{Languages:}
		\descriptList{Java 8/11/17, Typescript, Javascript} 
	\item\category{Build Tools:}
		\descriptList{Maven, NPM}
	\item\category{Framework:}
		\descriptList{SpringBoot, Camunda, Spring Data JPA, Hibernate, Spring Cloud, Angular 14/17, ExpressJs, Junit, Mockito, Test Containers} 
	\item\category{Databases:}
		\descriptList{Couchbase, Postgres, MongoDB, Redis}
	\item\category{Message Brokers:}
		\descriptList{RabbitMQ, Kafka}
	\item\category{AWS Cloud:}
		\descriptList{ECS Fargate, EC2, Auto Scaling, API Gateway, Load Balancer, Lambda, VPC, Route53, Cloud Watch, SQS, SNS, ElastiCache, OpenSearch}
	\item\category{Observability:}
		\descriptList{Elastic stack (ELK), Dynatrace}
	\item\category{CI/CD Tools:} Jenkins, Terraform, SonarQube, Liquibase
	\item\category{Others:} Shell Scripting, Linux commands
\end{tightemize}
\sectionsep

\pagebreak

\noindent\makebox[\linewidth]{
	\color{headings}
	\rule{1.0\linewidth}{1.0pt}
}

%%%%%%%%%%%%%%%%%%%%
%Certification Section%
%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}

\section{Certifications}
\subsection{AWS Developer Associate}
\descript{DVA-CO2}
\location{Dec 2024 – Present}
Score: 900
\columnbreak

\section{ }
\subsection{CDAC ACTS}
\descript{PG Diploma in Advance Computing (PG-DAC)}
\location{Jan 2020 – Feb 2021 | Pune, MH}
Grade: A
\columnbreak
\end{multicols}

\section{Education}
\subsection{Babaria Institute Of Technology}
\descript{Bachelor of Engineering in Electronics \& Communication}
\location{May 2016 | Vadodara, GJ}
CGPA: 7.84


\end{document}
